### 2024-06-18 index.qmd
links added to index

@@

We define the aims and methods in [preregistration plan](preregistration/preregistration.qmd).

@@

Data coding and extraction is described in data template [data/template.qmd](data/template.qmd).

>>>>

The public-facing version of the repository is available at
[https://tuomaseerola.github.io/metaMER/](https://tuomaseerola.github.io/metaMER/)

@@

We define the aims and methods in [preregistration plan](preregistration/preregistration.qmd), which has beeb preregistered at [OSF]().

@@

Data extraction is described in [extraction details](studies/extraction_details.qmd). See also [pass3 comparison ](studies/pass3_comparison.qmd).

The data will be parsed to tabular format using a custom [library_parser.qmd](studies/library_parser.qmd).
